---
title: "Bachelorette data"
author: "Mattie Johnson"
date: "1/12/2021"
output: html_document
---

```{r setup, include=FALSE}
#load necessary packages
library(tidyverse)
library(rvest)
library(rlist)
library(stringi)
library(htmltab)
```

Data related to the tv show is available on Wikipedia including the age, occupation, when they were eliminated, among others by season for all the contestents. There have been a total of 16 seasons.

#Contestant Information
```{r}
#consistent column names across seasons
my_renames <- function(name_from_wiki) {
  renames <- c(Job = "Occupation",Outcome = "Eliminated")
  renames[[name_from_wiki]]
}

#loops to scrape data tables from wikipedia
seasons_list<-list()
for (i in c(1:11,13:14)){
  season_data <- 
  read_html(paste0('https://en.wikipedia.org/wiki/The_Bachelorette_(season_',i,')')) %>%
  html_node(xpath = '//*[@id="mw-content-text"]/div[1]/table[2]') %>%
  html_table(fill = TRUE) %>% as.data.frame() %>% 
    mutate(season=i) %>% rename_at(vars(matches("^Job$|^Outcome$")), my_renames)
  seasons_list[[i]] <- season_data %>% select(Name, Age, Hometown, Occupation, Eliminated, season)
}
#season 12,15
for (i in c(12,15)){
  season_data <-  
    read_html(paste0('https://en.wikipedia.org/wiki/The_Bachelorette_(season_',i,')')) %>%
  html_node(xpath = '//*[@id="mw-content-text"]/div[1]/table[3]') %>%
  html_table(fill = TRUE) %>% as.data.frame() %>% 
    mutate(season=i) %>% rename_at(vars(matches("^Job$|^Outcome$")), my_renames)
  seasons_list[[i]] <- season_data %>% select(Name, Age, Hometown, Occupation, Eliminated, season)
}
#season 16
seasons_list[[16]] <- 'https://en.wikipedia.org/wiki/The_Bachelorette_(season_16)' %>%
  htmltab(2, rm_nodata_cols = F) %>%
  replace_na(list(Place = "", Ref = "")) %>%
  `rownames<-` (seq_len(nrow(.))) %>% 
  as.data.frame() %>% 
  rename_at(vars(matches("^Job$|^Outcome$")), my_renames) %>% 
  mutate(season=16) %>%
  select(Name, Age, Hometown, Occupation, Eliminated, season)
#combine all seasons into one dataset
contestant_data = do.call(rbind, seasons_list)

#reformat hometown into a column for city and state
contestant_data <- contestant_data %>% 
  mutate(From=Hometown) %>%
  separate(From,c("City", "State"), sep=",")
```

```{r}
#saving out data
#save(contestant_data,file="contestant_data.Rda")
```
When scraping wikipedia for 


#Bachelorette Information
In addition to information related to each of the men, this is a dataframe of available information related to the bachelorette of any given season.

```{r}

```